Spin canonical rings of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex
revise intro to inductive lemmas

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps for the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
	which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan' \in \BQ \otimes \di X$ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log spin canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%spin canonical divisors.

>>>>

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the inductive steps
for the proof of the main theorem: Theorem ~\ref{thm:main}. In
Subsection ~\ref{ssec:add-points} we prove three lemmas which
determine the generators and relations of $R_\halfcan = R_{\halfcan'
+ \frac{\alpha }{\beta}P}$ from those of $R_{\halfcan'}$, where
$\halfcan' \in \BQ \otimes \di X$ and $\frac{\alpha}{\beta} \in \BQ$. 
In Subsection ~\ref{ssec:raise-orders}, we prove an inductive lemma
allowing us to transfer information about the log spin canonical 
ring of a stacky curve to those of stacky curves with stabilizer
orders incremented by $2$ and fixed log divisor and stacky points.

%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%spin canonical divisors.
